Probabilistic Forecasting of Geomagnetic Indices using Gaussian Process Models

### 2017-08-30 revised-chapter.tex
Formatting changes
 - Moved OMNI to subsection of case study

\section{Data Source: OMNI}
The \emph{OMNI} data set is a collation of in-situ measurements taken by orbiting satellites and ground based measurements of geomagnetic indices. The data itself is represented as time averaged versions of the various quantities and is available at two frequencies, by hour and by minute. The quantities recorded can be broadly classified into two groups.

@@

\section{One Hour Ahead $Dst$ Prediction: Formulation} \label{sec:osa}

>>>>

@@

\section{One Hour Ahead $Dst$ Prediction} \label{sec:osa}

\subsection{Data Source: OMNI}
The \emph{OMNI} data set is a collation of in-situ measurements taken
by orbiting satellites and ground based measurements of geomagnetic
indices. The data itself is represented as time averaged versions of
the various quantities and is available at two frequencies, by hour
and by minute. The quantities recorded can be broadly classified into
two groups.

\subsection{Gaussian Process $Dst$ Model}
